\Large \bf Byteboy : A Byteman Companion application

### 2017-12-08 final-paper/paper.la_.tex
feat(paper): added limitations section

Discuss the limitations of our work.

@@

\bibitem{bytemanguide}
Byteman Programmer's Guide, 3.0.10, Apr 27, 2017
\\\texttt{http://downloads.jboss.org/byteman/\newline3.0.10/ProgrammersGuide.html}

>>>>

Currently, Byteboy has several limitations that confines it's use cases. For starters, Byteboy accepts a Java file with the extension {\tt .java} or {\tt .class} as input, however, many larger applications are not simply launched through the command-line using the {\tt java} command. Many popular Java applications may be packaged in {\tt .jar} format as an executable, or rely on larger build systems such as Maven and Gradle which makes the situation trickier.

The rules generated by Byteboy currently provide tracing and fuzz test capabilities, and this is reflective of our current product knowledge of Byteman and not the capabilities of Byteman as a tool. There are many more intricate and complicated types of rules that could be created, and using the data from our analysis it may allow for these rules to be created. However, it's difficult to create a code generator for a language when we aren't masters of the language ourselves, so this limited functionality should be seen as a proof of concept, and open the doors to future improvements in this application.

Lastly, the fuzz test generator only handles primitive data types at the moment, and doesn't work with arrays. The ability to fuzz arrays would be an interesting addition of functionality for the future, and allowing for the fuzzing of Java-specific data types (or even custom data types) would be an interesting topic of research as well.

@@

\bibitem{bytemanguide}
Byteman Programmer's Guide, 3.0.10, Apr 27, 2017
\\\texttt{http://downloads.jboss.org/byteman/\newline 3.0.10/ProgrammersGuide.html}
